---
title: "GARCH"
date: "2020/6/6"
output: html_document
---

```{r message=FALSE, warning=FALSE}
library(quantmod)
suppressWarnings(library(Metrics))
suppressWarnings(library(forecast))
suppressWarnings(library(tseries))
suppressWarnings(library(hts))
suppressWarnings(library(stringr))
suppressWarnings(library(xts))
suppressWarnings(library(imputeTS))
suppressWarnings(library(dplyr))
library(fGarch)
library(zoo)
library(FinTS)
library(prophet)
Sys.setlocale(category = "LC_ALL", locale = "english")
library(rugarch)

```

```{r }
suppressWarnings(getSymbols("NWSA",from="2015-1-1",to="2020-6-5"))
suppressWarnings(getSymbols("DIS",from="2015-1-1",to="2020-6-5"))
suppressWarnings(getSymbols("NFLX",from="2015-1-1",to="2020-6-5"))
suppressWarnings(getSymbols("GOOGL",from="2015-1-1",to="2020-6-5"))
suppressWarnings(getSymbols("T",from="2015-1-1",to="2020-6-5"))
head(GOOGL)
```

```{r }
GOOGL <- data.frame(GOOGL)
GOOGL$date <- row.names(GOOGL)
GOOGL.train <- GOOGL[GOOGL$date>='2015-01-02' & GOOGL$date<='2020-01-02','GOOGL.Close']
GOOGL.train.date <- GOOGL[GOOGL$date>='2015-01-02' & GOOGL$date<='2020-01-02','date']
GOOGL.test <- GOOGL[GOOGL$date>='2020-01-03' & GOOGL$date<='2020-01-31','GOOGL.Close']
GOOGL.test.date <- GOOGL[GOOGL$date>='2020-01-03' & GOOGL$date<='2020-01-31','date']
GOOGL.train.LastPrice <- GOOGL[GOOGL$date=='2020-01-02','GOOGL.Close']
h <- length(GOOGL.test)#20
plot(as.Date(GOOGL.train.date),GOOGL.train, type = "l",xlab='Time', ylab='GOOGL Stock Price')
```


```{r }
n <- length(GOOGL.train);
m <- length(c(GOOGL.train.LastPrice,GOOGL.test))
GOOGL.train.lr <- log(GOOGL.train[-1]/GOOGL.train[-n])
GOOGL.test.lr <- log(c(GOOGL.train.LastPrice,GOOGL.test)[-1]/c(GOOGL.train.LastPrice,GOOGL.test)[-m])
plot(as.Date(GOOGL.train.date[-1]),GOOGL.train.lr, type = "l", xlab='Time', ylab='GOOGL Log Return')
#GOOGL.train.lr[1:20]
length(GOOGL.test.lr) #20

```



```{r}
#Test
plot(as.Date(GOOGL.train.date[(n-500):n]),GOOGL.train.lr[(n-501):(n-1)], type = "l", xlab='Time', ylab='GOOGL Log Return', main="GOOGL Log Returns")

```

```{r}
par(mfrow=c(2,1))
plot(as.Date(GOOGL.train.date),GOOGL.train, type = "l",xlab='Time', ylab='GOOGL Stock Price')
plot(as.Date(GOOGL.train.date[-1]),GOOGL.train.lr, type = "l", xlab='Time', ylab='GOOGL Log Return')

```



```{r }
#Histogram
hist(GOOGL.train.lr, xlab="Daily log return of stock prices", prob=TRUE, ylim=c(0,30), main="Histogram for daily return of stock prices")
xfit<-seq(min(GOOGL.train.lr),max(GOOGL.train.lr),length=40)
yfit<-dnorm(xfit,mean=mean(GOOGL.train.lr),sd=sd(GOOGL.train.lr))
lines(xfit, yfit, col="blue", lwd=2)
```


```{r }
#QQ-plot
qqnorm(GOOGL.train.lr)
qqline(GOOGL.train.lr, col = 2) 
```

As seen from the histogram and the QQ-plot, the series has a somewhat normal distribution with fat tails at both ends.

```{r }
kpss.test(GOOGL.train.lr) 
```
H0: Stationary. Fail to reject the null. So stationary.


```{r }
acf(GOOGL.train.lr)
pacf(GOOGL.train.lr)
```

The ACF plot shows that since, the log stock price returns are not correlated, the mean is constant for the time series
Box-Ljung test H0: = “Serial Correlations are Zero”.

```{r }
## Ljung Box Tests
# y=GOOGL.train.lr-mean(GOOGL.train.lr)
Box.test(GOOGL.train.lr,lag=12,type='Ljung')
```

There are autocorrelation.


```{r }
t.test(GOOGL.train.lr)
```




According to Box-Ljung test the zero correlations hypothesis is not rejected. This is not an indication of ARCH effect.

```{r }
acf(GOOGL.train.lr^2)
pacf(GOOGL.train.lr^2)
```

PACF shows that the squared stock price return value is significant lag at lag 4. 


```{r }
arima1 <- auto.arima(GOOGL.train.lr,max.p = 5,max.q = 5,max.P = 5,max.Q = 5,max.d = 3,
                      trace = FALSE,stepwise = FALSE,seasonal = FALSE,ic = 'aicc')
arima1.res <- residuals(arima1)
arima1
```

```{r }
acf(arima1.res^2)
pacf(arima1.res^2)
```




```{r }
## Check residual
Box.test(arima1.res,lag=12,type='Ljung')
```
White noise residual

```{r }
## ARCH test1
# ArchTest(arima1.res - mean(arima1.res))
ArchTest(arima1.res,1)
```

There exists no arch effect.

```{r }
#test

```


```{r }
## ARCH test2
y=arima1.res-mean(arima1.res)
Box.test(arima1.res^2,lag=12,type='Ljung')
```

There exists no arch effect.

```{r }
acf(arima1.res^2)
pacf(arima1.res^2)
```


Try Arch(1)

```{r }
arch1=garchFit(~arma(1,2) +garch(1,0),data=GOOGL.train.lr,trace=F) 
summary(arch1)
```

```{r }
# plot(arch1)
```



All the parameters are significant.

The Jarquea Bera test is a goodness-of-fit test of whether sample data have the skewness and kurtosis matching a normal distribution. The null hypothesis for the test is that the data is normally distributed

The Shapiroâ Wilk test is a test of normality. The null hypothesis for the test is that the data is normally distributed

```{r }
par(mfrow=c(3,1))
resi=residuals(arch1,standardize=T)
plot(resi,xlab='year',ylab='stand-resi',type='l')
acf(resi,lag=20)
pacf(resi^2,lag=20)
```



```{r }
arch2=garchFit(~arma(1,2) +garch(1,0),data=GOOGL.train.lr,trace=F, cond.dist ='std') 
# summary(arch2)
```


```{r }
arch3=garchFit(~arma(1,2) +garch(1,0),data=GOOGL.train.lr,trace=F, cond.dist ='sstd') 
summary(arch3)
```

GARCH

```{r }
garch1=garchFit(~arma(1,2)+garch(1,1),data=GOOGL.train.lr,trace=F)
summary(garch1)
```

```{r }
# plot(garch1)
```


```{r }
garch2=garchFit(~arma(1,2)+garch(1,1),data=GOOGL.train.lr,trace=F, cond.dist ='std')
summary(garch2)
```

```{r }
par(mfcol=c(3, 1))
garch2.resi=residuals(garch2, standardize=T)
plot(garch2.resi, xlab="year" , ylab= "stand-resi" , type="l")
acf(garch2.resi, lag=20)
pacf(garch2.resi^2, lag=20)
```

```{r }
# plot(garch2)
```

```{r }
garch3=garchFit(~arma(1,2)+garch(1,1),data=GOOGL.train.lr,trace=F, cond.dist ='sstd')
summary(garch3)
```

```{r }
arch1.logPred <- predict(arch1, n.ahead = h, trace = FALSE, 
        plot=TRUE, nx=NULL, crit_val=NULL, conf=NULL)
```

```{r }
arch2.logPred <- predict(arch2, n.ahead = h, trace = FALSE, 
        plot=TRUE, nx=NULL, crit_val=NULL, conf=NULL)
```

```{r }
arch3.logPred <- predict(arch3, n.ahead = h, trace = FALSE, 
        plot=TRUE, nx=NULL, crit_val=NULL, conf=NULL)
```


```{r }
# garch2.logPred.roll=c()
# dat <- GOOGL.train.lr
# test <- GOOGL.test
# for (i in 1:h){
#     garch2=garchFit(~arma(1,2)+garch(1,1),data=dat,trace=F)
#     garch2.logPred <- predict(garch2, n.ahead = 1, trace = FALSE, 
#         plot=FALSE, nx=NULL, crit_val=NULL, conf=NULL)
#     arch1.logPred.roll <- append(garch2.logPred.roll, garch2.logPred, after = length(garch2.logPred.roll)) 
#     dat <- dat[-1]
#     dat <- c(dat,garch2.logPred)
#     
# }
```



```{r }
garch1.logPred <- predict(garch1, n.ahead = h, trace = FALSE, mse = 'cond',
        plot=TRUE, nx=NULL, crit_val=NULL, conf=NULL)
```


```{r }
garch2.logPred <- predict(garch2, n.ahead = h, trace = FALSE, 
        plot=TRUE, nx=NULL, crit_val=NULL, conf=NULL)
# garch2.logPred
```

```{r }
garch3.logPred <- predict(garch3, n.ahead = h, trace = FALSE, 
        plot=TRUE, nx=NULL, crit_val=NULL, conf=NULL)
```


```{r }
# Function for changing log return into price
Log2Price <- function(logData, initial_price) {
  logr <- c(0,logData)
  cuml_log= cumsum(logr)
  reconstructed_price_norm=exp(cuml_log)
  reconstructed_price = initial_price * reconstructed_price_norm
  reconstructed_price=reconstructed_price[-1]
  return(reconstructed_price)
}
```









```{r }
#Make predictions for Arch and Garch models
arch1.Pred <- Log2Price(arch1.logPred$meanForecast,GOOGL.train.LastPrice)
arch2.Pred <- Log2Price(arch2.logPred$meanForecast,GOOGL.train.LastPrice)
arch3.Pred <- Log2Price(arch3.logPred$meanForecast,GOOGL.train.LastPrice)
garch1.Pred <- Log2Price(garch1.logPred$meanForecast,GOOGL.train.LastPrice)
garch2.Pred <- Log2Price(garch2.logPred$meanForecast,GOOGL.train.LastPrice)
garch3.Pred <- Log2Price(garch3.logPred$meanForecast,GOOGL.train.LastPrice)
```


```{r }
# Evaluations
(arch1.smape <- suppressWarnings(smape(arch1.Pred,GOOGL.test)))
(arch2.smape <- suppressWarnings(smape(arch2.Pred,GOOGL.test)))
(arch3.smape <- suppressWarnings(smape(arch3.Pred,GOOGL.test)))
(garch1.smape <- suppressWarnings(smape(garch1.Pred,GOOGL.test)))
(garch2.smape <- suppressWarnings(smape(garch2.Pred,GOOGL.test)))
(garch3.smape <- suppressWarnings(smape(garch3.Pred,GOOGL.test)))
```

```{r }
#Test
#summary(arch1) #AIC       BIC       SIC      HQIC 
              #-5.633071 -5.608569 -5.633116 -5.623863 


#summary(arch2) #AIC       BIC       SIC      HQIC 
              #-5.809261 -5.780676 -5.809323 -5.798518 

#summary(garch1) #AIC       BIC       SIC      HQIC 
              #-5.661253 -5.632668 -5.661315 -5.650510 

#summary(garch2) #AIC       BIC       SIC      HQIC 
              #-5.863138 -5.830468 -5.863218 -5.850860 

```

```{r }
# Log Evaluations
(arch1.smape <- suppressWarnings(smape(arch1.logPred$meanForecast,GOOGL.test.lr)))
(arch2.smape <- suppressWarnings(smape(arch2.logPred$meanForecast,GOOGL.test.lr)))
(arch3.smape <- suppressWarnings(smape(arch3.logPred$meanForecast,GOOGL.test.lr)))
(garch1.smape <- suppressWarnings(smape(garch1.logPred$meanForecast,GOOGL.test.lr)))
(garch2.smape <- suppressWarnings(smape(garch2.logPred$meanForecast,GOOGL.test.lr)))
(garch3.smape <- suppressWarnings(smape(garch3.logPred$meanForecast,GOOGL.test.lr)))

```


```{r }
# Log Evaluations
plot(GOOGL.test.lr,type = "l")
plot(garch2.logPred$meanForecast,type = "l")
#plot(garch2@h.t,type = "l")
omega = garch1@fit$matcoef[1,1]
alpha = garch1@fit$matcoef[2,1]
beta = garch1@fit$matcoef[3,1]
sigma2 = omega + alpha * GOOGL.train.lr[n-1]^2 + beta*garch1@h.t[n-1]
sigma2
GOOGL.test.lr[1]
garch2.logPred$meanForecast
```


```{r }
#Performance plot for Arch
par(mfrow = c(1,1))
plot(as.Date(GOOGL.test.date), GOOGL.test, type = "l", pch=20, col="black",
     xlab="Date",ylab="Price", ylim=c(1300,1500),
     main="Garch & Arch predictions")

points(as.Date(GOOGL.test.date),arch2.Pred, pch=20, col="red")
points(as.Date(GOOGL.test.date),garch2.Pred, pch=20, col="blue")

legend("topleft", legend=c("Actual", "Arch","Garch"),
       col=c("black", "red","blue"), lty=1:3, cex=0.8)
```








# STL

```{r }
plot(mstl(GOOGL.train))
```

```{r }
#  "N"=none, "A"=additive, "M"=multiplicative and "Z"=automatically selected
ets1 <- ets(GOOGL.train,model = "ZZZ")
ets1
```

```{r }
ets1.pred <- forecast(ets1, h = h)
plot(ets1.pred)
```


```{r }
# Evaluation
ets1.smape <- suppressWarnings(smape(ets1.pred$mean,GOOGL.test))
ets1.smape
```


```{r }
#Performance plot for Arch
par(mfrow = c(1,1))
plot(as.Date(GOOGL.test.date), GOOGL.test, type = "l", pch=20, col="black",
     xlab="Date",ylab="Price", ylim=c(1300,1500),
     main="ETS predictions")

points(as.Date(GOOGL.test.date),ets1.pred$mean, pch=20, col="red")

legend("topleft", legend=c("Actual", "ETS"),
       col=c("black", "red"), lty=1:2, cex=0.8)
```







# Prophet

```{r }
df <- GOOGL[GOOGL$date>='2015-01-02' & GOOGL$date<='2019-12-31',c('date','GOOGL.Close')]
names(df) <- c('ds','y')
# df$cap <- 8.5
m <- prophet(df,daily.seasonality=TRUE)
```



```{r }
future <- make_future_dataframe(m, periods = h,freq='D')
# future$cap <- 8.5
fcst <- predict(m, future)
plot(m, fcst)
```

```{r }
prophet.pred <- fcst$yhat
n <- length(prophet.pred)
prophet.pred=prophet.pred[(n-h+1):n]
```

```{r }
# Evaluation
prophet1.smape <- suppressWarnings(smape(prophet.pred,GOOGL.test))
prophet1.smape
```


```{r }
#Performance plot for Arch
par(mfrow = c(1,1))
plot(as.Date(GOOGL.test.date), GOOGL.test, type = "l", pch=20, col="black",
     xlab="Date",ylab="Price", ylim=c(1300,1500),
     main="Prophet predictions")

points(as.Date(GOOGL.test.date),prophet.pred, pch=20, col="red")

legend("topleft", legend=c("Actual", "Prophet"),
       col=c("black", "red"), lty=1:2, cex=0.8)
```

Forecast by prophet isn’t ideal to use this forecast in trading







# ARIMA

```{r }
arima1.pred <- forecast(arima1,h)
arima1.LogPred <- arima1.pred$mean
arima1.pred <- Log2Price(arima1.LogPred,GOOGL.train.LastPrice)
arima1.pred
```


```{r }
# Evaluations
arima1.smape <- suppressWarnings(smape(arima1.pred,GOOGL.test))
arima1.smape

smape(arima1.LogPred,GOOGL.test.lr)
```


```{r }
#Performance plot for Arima
par(mfrow = c(1,1))
plot(as.Date(GOOGL.test.date), GOOGL.test, type = "l", pch=20, col="black",
     xlab="Date",ylab="Price", ylim=c(1300,1500),
     main="Arima predictions")

points(as.Date(GOOGL.test.date),arima1.pred, pch=20, col="red")

legend("topleft", legend=c("Actual", "Arima"),
       col=c("black", "red"), lty=1:2, cex=0.8)
```

```{r }
garch2.logPred <- predict(garch2, n.ahead = h, trace = FALSE, 
        plot=TRUE, nx=NULL, crit_val=NULL, conf=NULL)
# garch2.logPred
```



```{r }
c('Arch',arch1.smape)
c('Garch',garch1.smape)
c('Prophet',prophet1.smape)
c('Arima',arima1.smape)
```



```{r }

```
